Asteroid project summary

### 2021-11-11 summaries/21-11/21-11.tex
Pulled sigma data

\draw[-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
\draw[-{Latex[length=3mm]}] (0, 0) -- (4, 0.5) node[anchor=south] {$\unit Y$};
\draw[-{Latex[length=3mm]}] (0, 0) -- (-2, 3) node[anchor=south] {$\unit Z$};

\draw (0.5, -0.75) arc (290:310:1.5);
\draw (0.9, -0.9) node[anchor=center] {$\alpha$};

@@

\draw (0.95, -0.5) arc (320:361:1);
\draw (1.4, -0.25) node[anchor=center] {$\gamma$};

>>>>

\draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
\draw[thick,-{Latex[length=3mm]}] (0, 0) -- (4, 0.5) node[anchor=south] {$\unit Y$};
\draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-2, 3) node[anchor=south] {$\unit Z$};

\draw (0.5, -0.75) arc (290:302:2.5);
\draw (0.9, -0.9) node[anchor=center] {$\alpha$};

@@

\draw (0.97, -0.52) arc (330:360:1.3);
\draw (1.4, -0.25) node[anchor=center] {$\gamma$};
